Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Minor

```{r alpha-MAP scatter plots, fig.width=10, fig.height=4}
ggplot((dset.alpha, aes(x=diversities_shannon, y=MAP)) +
    facet_wrap(BL_AGE_GROUP, ncol=4, scales = "free") +
    geom_point(size=0.1, shape=1, aes(colour = SEX)) +
    geom_smooth(method=lm, se=TRUE, size=0.5, color = 'Black') +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y = 0,
                 parse = TRUE,
                 size = 3) +   
    ylim(0, 200) +
    ggplot2::theme_minimal() 
```

>>>>

```{r alpha-MAP scatter plots, fig.width=10, fig.height=4}
ggplot((dset.alpha %>% mutate(SEX = factor(ifelse(SEX == 0, "Male", "Female")))),
       aes(x=diversities_shannon, y=MAP)) +
    facet_wrap(~BL_AGE_GROUP + SEX, ncol=2, scales = "free") +
    geom_point(size=0.1, shape=1, aes(colour = ANYDRUG)) +
    geom_smooth(method=lm, se=TRUE, size=0.5, color = 'Black') +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y = 0,
                 parse = TRUE,
                 size = 3) +   
    ylim(0, 200) +
    ggplot2::theme_minimal() 
```
